% ================================================================================================
%         												Kipp van Schooten - LaTeX CV
%
%  Filename:       KJvS_CV.tex
%  Author:         Kipp J van Schooten (kippvs@gmail.com)
%  Version:        0.0.3
%  Date:           2014-09-14 - 2014-09-16
%
%  Description:    o TeX file for building Kipp van Schooten's CV
%
%	 Notes:					 o Cobbled together from open access documents authored by:
%												Paul D. Gessler (https://github.com/pdgessler)
%												Theodore P. Pavlic (http://www.tedpavlic.com)
%									 o Several commands are probably superfluous and remain from
%												merging two .TeX files and making significant changes
%									 o If you find this file useful for your own needs, please
%												include references to the above sources in your .TeX
%
% ================================================================================================
\documentclass[11pt,letterpaper]{article}

\def\myauthor{Kipp J. van Schooten}
\def\mytitle{Kipp J. van Schooten, PhD - CV}
\def\myemail{kippvs@gmail.com}
\def\myweb{kippvs}
\def\myphone{1-555-555-5555}
\def\myfax{1-555-555-5555}
\def\mykeywords{kipp van schooten, 
								resume, 
								curriculum, 
								vitae, 
								curriculum vitae, 
								cv, 
								kippvs, 
								kipp, 
								van schooten
								}

\usepackage{url}
\usepackage{xcolor}
		\definecolor{darkred}{rgb}{102,0,0} 
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[shortlabels]{enumitem}
		\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=1.125in,
						right=1in,
						left=2in]{geometry}
\usepackage[strict]{changepage}
\usepackage[ocgcolorlinks,
						urlcolor={[rgb]{0,0,0.54}},
						unicode,
						plainpages=false,
						pdfpagelabels,
						pdftitle={\mytitle},
						pdfauthor={\myauthor},
						pdfkeywords={\mykeywords}]{hyperref}
\usepackage{doi}
% To change the text before the DOI, adjust this command
%\renewcommand\doitext{doi:}

% ================================================================================================
\newcommand{\ML}{\textsc{Matlab}}
\newcommand\CPP{C/C\ensuremath{+}\ensuremath{+}}

\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily\small #1}}
\newcommand{\rdate}[1]{{\addfontfeature{Numbers=OldStyle} \hfill #1}}
\renewcommand{\date}[1]{{\addfontfeature{Numbers=OldStyle} #1}}
\renewcommand{\labelitemi}{-} 

\setmainfont[
				Ligatures={TeX,Common},
				BoldFont={AGaramondPro-Bold},
				]{Adobe Garamond Pro}
\setsansfont[
				Ligatures={TeX,Common},
				Letters=SmallCaps,
				Color=darkred,
				]{Adobe Garamond Pro}
\setmonofont{FontAwesome}

% Get rid of indenting throughout entire document
\setlength\parindent{0pt}

% Setup aligned list
\newenvironment{itemize*}
{\begin{itemize}
  \setlength{\itemsep}{0pt}}
{\end{itemize}}

% ================================================================================================
% Simpler bibsections for CV sections (thanks to natbib for inspiration)
%
% * For lists of references with hanging indents and no numbers:
%
%   \begin{bibsection}
%       \item ...
%   \end{bibsection}
%
% * For numbered lists of references (with hanging indents):
%
%   \begin{bibenum}
%       \item ...
%   \end{bibenum}
%
%   Note that bibenum numbers continuously throughout. To reset the
%   counter, use
%
%   \restartlist{bibenum}
%
%   at the place where you want the numbering to reset.
% ================================================================================================
\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=, 
				leftmargin=\bibhang,%
        itemindent=-\bibhang,
        %itemsep=\bibsep, 
				itemsep=5pt, 
				parsep=\z@, 
				partopsep=0pt, 
				topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*], 
				resume, 
				leftmargin={\bibhang},%
        itemindent=\bibhang,
        %itemsep=\bibsep, 
				itemsep=5pt, 
				parsep=\z@, 
				partopsep=0pt, 
				topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

% ================================================================================================
%				MAKE DOCUMENT HEADER
% ================================================================================================
\begin{document}\flushbottom
\pagestyle{fancy} \setlength\headwidth{6.5in}
\rhead{\textsc{kipp j.~van schooten—curriculum vitæ—\thepage{} of \pageref*{LastPage}}} \cfoot{}
\thispagestyle{empty}
\begin{adjustwidth}{-1in}{}
{\Huge
  {\textsc{%
    {\addfontfeature{Style=TitlingCaps}K}\kern-1.5ptipp 
    {\addfontfeature{Style=TitlingCaps}J}\kern-2pt. van 
    {\addfontfeature{Style=TitlingCaps}S}chooten, 
		{\addfontfeature{Style=TitlingCaps}P}h.{\addfontfeature{Style=TitlingCaps}D}.}
  }
}
\vspace{0.25em} % buffer layer
{\footnotesize
  {\textsc{%
		\newline University of Utah, Department of Physics \& Astronomy, 115 S. 1400 E., Salt Lake City, UT 84112-0830}
		\newline [\textsc{cell}: \href{tel:\myphone}{\myphone}]~~~~
						[\textsc{fax}: \href{tel:\myfax}{\myfax}]~~~~
						[\href{mailto:\myemail}{\myemail}]~~~~
						[\href{http://www.physics.utah.edu/~kippvs/}{www.physics.utah.edu/$\sim$kippvs}]~~~
						\href{https://www.github.com/\myweb}{\texttt{}}~~~
						\href{https://www.linkedin.com/in/kippvs\myweb}{\texttt{}}
  }
}
\par
\hrulefill
\end{adjustwidth}  
\reversemarginpar 
\setlength\marginparwidth{0.85in}
\medskip

% ================================================================================================
% 			RESEARCH INTERESTS
% ================================================================================================
\mhead{Research \newline Interests}%
Investigating fundamental spin-spin interactions as a probe of the nano- and mesoscale physics governing macroscopic observables in material systems ranging from organic semiconductors to colloidal quantum dots. By coherently manipulating the spin identity of optically and electrically generated excited states via electron spin resonance (ESR), insight into their chemical nature, environmental interactions, and possible technological usefulness can be gained.
\\[5pt]
Also of interest is the technological development of novel and unique experimental probes of such spin states. Combining magnetic resonance techniques with modern advancements in the realms of electronics, optical spectroscopy, and radio frequency control opens new windows on accessing and controlling spin systems.
\\[5pt]
Current projects focus on the exploration of spin dynamics in organic semiconductorsand occurrs on two fronts: First, by examining the mechanisms responsible for spin- to charge-current conversion in organics via ferromagnetic resonance-pumped inverse spin Hall effect. Second, electrically-detected magnetic resonance is used to probe local spin-spin interactions, either between charge-carrier pairs or between charge carriers and their local nuclear environment.
\vspace{0.4\baselineskip} % add a bit of space after list

% ================================================================================================
% 			RESEARCH EXPERIENCE
% ================================================================================================
\mhead{Research \newline Experience}
\vspace{-1.1em} % horizontally align header and list
\begin{bibsection}

		\item \textbf{Postdoctoral Researcher}, University of Utah, Salt Lake City, Utah \rdate{2013–\textsc{present}}
		\vspace{-0.5em} % horizontally align header and list
		
		\item \href{http://www.mrsec.utah.edu/}{\emph{Materials Research, Science, and Engineering Center (MRSEC)}}
					\begin{itemize*}
							\item Develop powerful excitation and detection methods for the Inverse Spin Hall Effect.
							\item Explore spin-current injection schemes and spin- to charge-current conversion mechanisms in organic semiconductors.
							\item Design and implement a $\sim$\$1.4M, 12.5 Tesla, 330 GHz electro-optical spin resonance facility. [\href{http://www.physics.utah.edu/~kippvs/papers/UtahMRSEC_HighField_NoQuotes.pdf}{PDF}] (\textit{project shelved due to \href{http://www.sltrib.com/sltrib/news/57001654-78/ustar-audit-created-jobs.html.csp}{withdrawal of USTAR fund-matching}})
							\item Advisors: Profs. Christoph Boehme, Z. Valy Vardeny, Brian Saam, Joel S. Miller
					\end{itemize*}

		\item \href{http://www.physics.utah.edu/~boehmelab/}{\emph{The Spin Electronics Group}}
					\begin{itemize*}
							\item Measuring spin-spin interaction energies and pair separations within organic semiconductors via electrical detection of Rabi oscillations under detuning.
							\item Correlating morphology and magnetic order/disorder in organic semiconductors.
							\item Develop and refine the measurement and excitation techniques required for observation of excedingly small electrical and optical signals.
							\item Advisor: Prof. Christoph Boehme
					\end{itemize*}
		
		\item \href{http://www.physik.uni-regensburg.de/forschung/lupton/lupton/}{\emph{The Organic Semiconductors and Optical Nanostructures Group}}
					\begin{itemize*}
							\item Spent 4 weeks at the University of Regensburg, Regensburg, Germany to retrofit a wide-field, optical microscopy setup with single-molecule spin-resonance capabilities.
							\item This work was sponsored by Prof. John M. Lupton, now Chair of the Institute of Experimental and Applied Physics at the University of Regensburg.
					\end{itemize*}
					
\end{bibsection}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			EDUCATION
% ================================================================================================
\mhead{Education}
\vspace{-1.1em} % horizontally align header and list
\begin{bibsection}

		\item \href{http://www.utah.edu/}{\textbf{University of Utah}}, Salt Lake City, Utah \rdate{2006–2012}\newline
					\emph{Ph.D. in Condensed Matter Physics, \href{http://www.physics.utah.edu/}{Dept. of Physics \& Astronomy}}
					\begin{itemize*}
							\item Thesis: \textit{Optically Active Charge Traps and Chemical Defects in Semiconducting Nanocrystals Probed by Pulsed Optically Detected Magnetic Resonance} [\href{http://www.physics.utah.edu/~kippvs/papers/Kipp_van_Schooten_Thesis.pdf}{PDF}]
							\item Advisor: Prof.~John M.~Lupton
					\end{itemize*}

		\item \href{http://www.spsu.edu//}{\textbf{Southern Polytechnic State University}}, Marietta, Georgia \rdate{2000–2005}\newline
					\emph{B.Sc in Physics, \href{http://www.spsu.edu/physics/}{Dept. of Physics}}
					\begin{itemize*}
							\item Minor (non-traditional) in Electrical Engineering Technology
							\item Senior Project: \textit{Development of a Wireless Geophone System for Subsurface Depth Seismology}
							\item Advisors: Dr. James B. Whitenton, Dr. Russel S. Patrick, Dr. Michael G. Thackston
					\end{itemize*}
					
\end{bibsection}
\vspace{0.95\baselineskip} % add a bit of space after list

% ================================================================================================
% 			TECHNICAL SKILLS
% ================================================================================================
\mhead{Technical \newline Proficiencies}
\vspace{-1.3em} % horizontally align header and list
\begin{bibsection}

		\item \emph{Techniques}%
					\begin{itemize*}
							\item Electron Spin Resonance (electrical, optical, and absorption detected ESR, both at high and low fields)
							\item Optical techniques (pulsed electrical/optical excitation for time-gated electroluminescence/photoluminescence spectroscopy)
							\item Electronic methods of small-signal detection and signal conditioning
							\item Organic semiconductor device fabrication, glovebox procedures, and thermal evaporation of metals
							\item Basic chemical handling, wetlab, and cleanroom procedures
							\item Basic analog/digital electronics, microcontroller programming/interfacing, RF electronics, and associated test equipment
					\end{itemize*}
					
		\item \emph{Software}
					\begin{itemize*}
							\item OriginLab, Python, LabVIEW, Xepr/PulseSPEL, \LaTeX{}
							\item Working experience in AutoCAD/Inventor, Assembly, \ML{}, \CPP{}
					\end{itemize*}
					
\end{bibsection}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			PUBLICATIONS
% ================================================================================================
\mhead{Refereed\newline Journal\newline Publications}
\vspace{-1.1em} % horizontally align header and list
\begin{bibenum}

		\item Malissa, H., Kavand, M., Waters, D. P., \textbf{van Schooten, K. J.}, Burn, P. L., Vardeny, Z. V., Saam, B., Lupton, J. M., Boehme, C., Room-temperature coupling between electrical current and nuclear spins in OLEDs. \textit{Science} (2014) [\textit{in press}]

		\item \textbf{van Schooten, K. J.}, Boehme, C. \& Lupton, J. M. Coherent magnetic resonance of nanocrystal quantum-dot luminescence as a window to blinking mechanisms. \textit{ChemPhysChem} \textbf{15}, 1737--46 (2014). \doi{10.1002/cphc.201400081} [\href{http://www.physics.utah.edu/~kippvs/papers/2014_ChemPhysChem.pdf}{PDF}]

		\item Her, J. H., Stephens, P. W., Davidson, R. A., Min, K. S., Bagnato, J. D., \textbf{van Schooten, K. J.}, Boehme, C. \& Miller, J. S.	Weak ferromagnetic ordering of the Li\textsuperscript{+}[TCNE]\textsuperscript{\textbullet -} (TCNE = tetracyanoethylene) organic magnet with an interpenetrating diamondoid structure. \textit{J. Am. Chem. Soc.} \textbf{135}, 18060--3 (2013) \doi{10.1021/ja410818e} [\href{http://www.physics.utah.edu/~kippvs/papers/2013_JACS.pdf}{PDF}]
		
		\item \textbf{van Schooten, K. J.}, Huang, J., Talapin, D. V, Boehme, C. \& Lupton, J. M. Spin-dependent electronic processes and long-lived spin coherence of deep-level trap sites in CdS nanocrystals. \textit{Phys. Rev. B} \textbf{87}, 125412 (2013) \doi{10.1103/PhysRevB.87.125412} [\href{http://www.physics.utah.edu/~kippvs/papers/2013_PRB.pdf}{PDF}]
		
		\item \textbf{van Schooten, K. J.}, Huang, J., Baker, W. J., Talapin, D. V, Boehme, C. \& Lupton, J. M. Spin-dependent exciton quenching and spin coherence in CdSe/CdS nanocrystals. \textit{Nano Lett.} \textbf{13}, 65--71 (2013) \doi{10.1021/nl303459a} [\href{http://www.physics.utah.edu/~kippvs/papers/2013_NanoLett.pdf}{PDF}]

		\item Baker, W. J., Ambal, K., Waters, D. P., Baarda, R., Morishita, H., \textbf{van Schooten, K. J.}, McCamey,
D. R., Lupton, J. M. \& Boehme, C. Robust absolute magnetometry with organic thin-film devices. \textit{Nat. Commun.} \textbf{3}, 898 (2012) \doi{10.1038/ncomms1895} [\href{http://www.physics.utah.edu/~kippvs/papers/2012_NatComm.pdf}{PDF}]

		\item Baker, W. J., McCamey, D. R., \textbf{van Schooten, K. J.}, Lupton, J. M. \& Boehme, C. Differentiation between polaron-pair and triplet-exciton polaron spin-dependent mechanisms in organic light-emitting diodes by coherent spin beating. \textit{Phys. Rev. B} \textbf{84}, 165205 (2011) \doi{10.1103/PhysRevB.84.165205} [\href{http://www.physics.utah.edu/~kippvs/papers/2011_PRB.pdf}{PDF}]
		
		\item Chaudhuri, D., Wettach, H., \textbf{van Schooten, K. J.}, Liu, S., Sigmund, E., H\"{o}ger, S. \& Lupton, J. M. Tuning the singlet-triplet gap in metal-free phosphorescent $\pi$--conjugated polymers. \textit{Angew. Chem.} \textbf{49}, 7714--17 (2010) \doi{10.1002/anie.201003291} [\href{http://www.physics.utah.edu/~kippvs/papers/2010_Angew.pdf}{PDF}]
		
		\item McCamey, D. R., \textbf{van Schooten, K. J.}, Baker, W. J., Lee, S.-Y., Paik, S.-Y., Lupton, J. M. \& Boehme, C. Hyperfine-Field-Mediated Spin Beating in Electrostatically Bound Charge Carrier Pairs. \textit{Phys. Rev. Lett.} \textbf{104}, 017601 (2010) \doi{10.1103/PhysRevLett.104.017601} [\href{http://www.physics.utah.edu/~kippvs/papers/2010_PRL.pdf}{PDF}]
		
		\item Boehme, C., McCamey, D. R., \textbf{van Schooten, K. J.}, Baker, W. J., Lee, S.-Y., Paik, S.-Y. \& Lupton, J. M. Pulsed electrically detected magnetic resonance in organic semiconductors. \textit{Phys. Status Solidi B} \textbf{246}, 2750--2755 (2009) \doi{10.1002/pssb.200982357} [\href{http://www.physics.utah.edu/~kippvs/papers/2009_PSSb.pdf}{PDF}]
		
		\item Walter, M. J., Borys, N. J., \textbf{van Schooten, K. J.} \& Lupton, J. M. Light-Harvesting Action Spectroscopy of Single Conjugated Polymer Nanowires. \textit{Nano Lett.} \textbf{8}, 3330--3335 (2008) \doi{10.1021/nl801757p} [\href{http://www.physics.utah.edu/~kippvs/papers/2008_NanoLett.pdf}{PDF}]

\end{bibenum}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			PRESENTATIONS
% ================================================================================================
\mhead{Conference\newline Talks}
\vspace{-1.1em} % horizontally align header and list
\begin{bibenum}

		\item \textbf{van Schooten, K. J.}, Sun, D., Vardeny, Z. V., \& Boehme, C. Artifact free Inverse Spin Hall Effect Measurements in Organic Semiconductor Devices by Pulsed Ferromagnetic-Resonant Spin-Pumping. \textit{Rocky Mountain Conference on Magnetic Resonance} (RMCAC 2014). Copper Mountain, Colorado, USA, July 13--17, 2014.

		\item \textbf{van Schooten, K. J.}, Huang, J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Spin-Dependent Light-Harvesting in Nanotetrapods by Controlling Electronic Trap States with Optically Detected Magnetic Resonance. \textit{Nanoscience with Nanocrystals} (NaNaX6). Bad Hofgastein, Austria, May 18--23, 2014.
		
		\item \textbf{van Schooten, K. J.}, Huang, J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Spin-Dependent Light-Harvesting in Nanotetrapods by Controlling Electronic Trap States with Optically Detected Magnetic Resonance. \textit{International Conference on Quantum Dots} (QD2014). Pisa, Italy, May 11--16, 2014.
		
		\item \textbf{van Schooten, K. J.}, Huang, J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Spin-Dependent LightHarvesting in Colloidal Nanocrystals by Controlling Electronic Trap States with Optically Detected Magnetic Resonance. \textit{American Physical Society March Meeting}. Baltimore, Maryland, USA, March 17--22, 2013.
		
		\item \textbf{van Schooten, K. J.}, Huang, J., Baker, W. J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Probing Electronic Trap States in Colloidal Nanocrystals with Optically Detected Magnetic Resonance. \textit{Rocky Mountain Conference on Analytical Chemistry} (RMCAC 2012). Copper Mountain, Colorado, USA, June 16--21, 2012.
		
		\item \textbf{van Schooten, K. J.}, Baker, W. J., Huang, J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Observation of Long Spin Coherence Times in CdSe/CdS Colloidal Nanostructures. \textit{American Physical Society March Meeting}. Dallas, TX, USA, March 22--25, 2011.

\end{bibenum}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			POSTERS
% ================================================================================================
\mhead{Conference\newline Posters}
\vspace{-1.1em} % horizontally align header and list
\begin{bibenum}

		\item \textbf{van Schooten, K. J.}, Baker, W. J., Huang, J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Long Spin Coherence Lifetimes of Optically Generated Excitations in Colloidal CdS Nanorods. \textit{Optical Probes of Conjugated Polymers and Organic Nanostructures} (OP2011) \& \textit{Excited State Processes on Electronic and Bio Nanomaterials} (ESP2011). Santa Fe, NM, USA, June 19--24, 2011
		
		\item \textbf{van Schooten, K. J.}, Huang, J., Baker, W. J., Talapin, D. V., Boehme, C. \& Lupton, J. M. Long Spin Coherence Lifetimes of Optically Generated Excitations in Colloidal CdS Nanorods. \textit{Fundamental Optical Processes in Semiconductors} (FOPS2011). Lake Junaluska, NC, USA, August 1--5, 2011.
		
		\item \textbf{van Schooten, K. J.}, Liu, S., Walter, M. J., McCamey, D. R., Scherf, U., Boehme, C., \& Lupton, J. M. Time-Resolved Measurements of Spin-Dependent Carrier Recombination in Charge Transfer States of pi-Conjugated Polymers. \textit{237th American Chemical Society National Meeting}. Salt Lake City, UT, USA, March 22--26, 2009.

\end{bibenum}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			COLLOQUIA & SEMINARS
% ================================================================================================
\mhead{Colloquia \&\newline Seminars}
\vspace{-1.1em} % horizontally align header and list
\begin{bibenum}

		\item Making Use of Trapped-Carrier Spins in Colloidal Nanocrystals, \textit{Institute of Experimental and Applied Physics Colloqium}, University of Regensburg, Regensburg, Germany, June, 23, 2014.
		
		\item Increasing Accessibility to the Inverse Spin Hall Effect by Pulsed Ferromagnetic-Resonant Spin-Pumping, \textit{Materials Research, Science, and Engineering Center} (MRSEC) \textit{Seminar}, University of Utah, Salt Lake City, UT, USA, April 8, 2014.

\end{bibenum}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			BOOKS
% ================================================================================================
\mhead{Books}
\vspace{-1.1em} % horizontally align header and list
\begin{bibenum}

		\item \textbf{K. J. van Schooten}, \textit{Optically Active Charge Traps and Chemical Defects in Semiconducting Nanocrystals Probed by Pulsed Optically Detected Magnetic Resonance}, Springer, Cham, Switzerland, 2013. ISBN$\colon$9783319005898

\end{bibenum}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			IN PREPARATION
% ================================================================================================
\mhead{Papers in\newline Preparation}
\vspace{-1.1em} % horizontally align header and list
\begin{bibenum}

		\item \textbf{van Schooten, K. J.}, Baird, D. L., Limes, M. E., Lupton, J. M., Boehme, C. Probing spin-spin interactions in intermolecular electron-hole pairs of a conjugated polymer through electrically detected spin-beating (2014) [\textit{under review}]
		
		\item Sun, D., \textbf{van Schooten, K. J.}, Malissa, H., Kavand, M., Boehme, C., Vardeny, Z. V. Spin-orbit dependence of spin-Hall angles in organic semiconductors [\textit{in preparation}]

\end{bibenum}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			ACADEMIC SERVICE
% ================================================================================================
\mhead{Academic \newline Service}
\vspace{-1.1em} % horizontally align header and list
\begin{bibsection}

		\item \textbf{Graduate Student Advisory Council, Chair}\rdate{2011-2012}\newline
		College of Science, University of Utah, Salt Lake City, Utah
		
		\item \textbf{Graduate Student Advisory Council, Vice-Chair}\rdate{2010-2011}\newline
		College of Science, University of Utah, Salt Lake City, Utah

		\item \textbf{Academic Misconduct Committee, Graduate Representative}\rdate{2008-2010}\newline
		College of Science, University of Utah, Salt Lake City, Utah
		
		\item \textbf{Academic Appeals Committee, Graduate Representative}\rdate{2008-2010}\newline
		College of Science, University of Utah, Salt Lake City, Utah
		
		\item \textbf{IEEE Student Organization, Activities Director}\rdate{2002-2003}\newline
		Electrical and Computer Engineering Technology, Southern Polytechnic State University, Marietta, Georgia
		
\end{bibsection}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			TEACHING EXPERIENCE
% ================================================================================================
\mhead{Teaching \newline Experience}
\vspace{-1.1em} % horizontally align header and list
\begin{bibsection}

		\item \textbf{University of Utah}, Salt Lake City, Utah \rdate{2006–2009}\newline
					\emph{Graduate Teaching Assistant, Dept. of Physics \& Astronomy}
					\begin{itemize*}
							\item Courses:  Modern Physics (grading, office hours, class 1 day/week), Electronics I (grading, office hours, practical lab), Solid State II (grading, office hours)
							\item \textit{Outstanding Teaching Assistant of the Year} award winner each year with TA duties
					\end{itemize*}

		\item \textbf{Southern Polytechnic State University}, Marietta, Georgia \rdate{2003–2005}\newline
					\emph{University Staff Tutor, Campus-wide}
					\begin{itemize*}
							\item Courses: Physics (all levels), Calculus (\textsc{I}-\textsc{III}), Pre-Calculus
							\item Hired as the only staff Physics tutor for the University, and one of two Calculus tutors
					\end{itemize*}
					
\end{bibsection}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			HONORS AND AWARDS
% ================================================================================================
\mhead{Honors \& \newline Awards}
\vspace{-1.1em} % horizontally align header and list
\begin{bibsection}

		\item \textbf{Ph.D. dissertation published in Springer Theses Series}\rdate{\textsc{spring} 2013}\newline \textit{Optically Active Charge Traps and Chemical Defects in Semiconducting Nanocrystals Probed by Pulsed Optically Detected Magnetic Resonance}, ISBN$\colon$9783319005898
		
		\item \textbf{2nd Place Best Graduate Student Oral Presentation}\rdate{\textsc{august} 4, 2012}\newline \textit{Probing Electronic Trap States in Colloidal Nanocrystals with Optically Detected Magnetic Resonance}. Student Research Symposium, Dept. Physics \& Astronomy, University of Utah
		
		\item \textbf{1st Place Best Graduate Student Oral Presentation}\rdate{\textsc{august} 13, 2011}\newline \textit{Long Spin Coherence Lifetimes of Optically Generated Excitations in Colloidal CdS Nanorods}. Student Research Symposium, Dept. Physics \& Astronomy, University of Utah
		
		\item \textbf{Outstanding Teaching Assistant}\rdate{2008-2009}\newline Course: Solid State Physics II (PHYS 5520). Taught by: Prof. John Lupton. Dept. Physics \& Astronomy, University of Utah

		
		\item \textbf{Outstanding Teaching Assistant}\rdate{2007-2008}\newline Course: Intro to Quantum and Relativity (PHYS 3740). Taught by: Prof. John Lupton. Dept. Physics \& Astronomy, University of Utah

		
		\item \textbf{Outstanding Teaching Assistant}\rdate{2006-2007}\newline Course: Intro to Quantum and Relativity (PHYS 3740). Taught by: Prof. John Lupton. Dept. Physics \& Astronomy, University of Utah

		
		\item \textbf{Outstanding Teaching Assistant}\rdate{2005-2006}\newline Course: Intro to Quantum and Relativity (PHYS 3740). Taught by: Prof. David Ailion. Dept. Physics \& Astronomy, University of Utah

\end{bibsection}
\vspace{\baselineskip} % add a bit of space after list

% ================================================================================================
% 			PROFESSIONAL AFFILIATIONS
% ================================================================================================
\mhead{Professional \newline Affiliations}%
American Physical Society, Member \rdate{2008–\textsc{present}}\newline
American Chemical Society, Member \rdate{2006-\textsc{present}}

% ================================================================================================
\end{document}
% ================================================================================================